Hydras \& Co.

### 2023-11-09 doc/chapter-primrec.tex
Remove the notation for empty vectors of PR functions
Replaced misc.inj_right_pair2 with stdlib's Eqdep_dec.inj_pair2_eq_dec

@@

This function is an instance of the primitive recursion scheme,
with $n=1$, $g$ the constant unary function which returns $0$ (see subsection~\vref{sect:k0}),
 and $h$ the function defined by $h(p,x,n_1)=x+n_1$, which can be written as the composition of $+$ and the projections 
$\pi_{2,3}$ and $\pi_{3,3}$ (the three of them  being  primitive recursive).

>>>>

% If we consider any value of $n$, the same construction
% builds the constant function of type $\mathbb{N}^n \arrow \mathbb{N}$ which returns $0$.

\subsubsection{Constant functions}

Let $k$ be some natural number; the unary constant function which always returns $k$ is built through $k$ nested compositions of the 
successor function to the  unary constant function which returns $0$.

@@

This function is an instance of the primitive recursion scheme,
with $n=1$, $g$ is the constant unary function which returns $0$ (see subsection~\vref{sect:k0}),
 and $h$ the function defined by $h(p,x,n_1)=x+n_1$, which can be written as the composition of $+$ and the projections 
$\pi_{2,3}$ and $\pi_{3,3}$ (the three of them  being  primitive recursive).
